% !TEX program = lualatex
\documentclass[a4paper,11pt]{article}
\usepackage{fontspec}
\usepackage{url,parskip,color,graphicx,xcolor,geometry,tabularx,enumitem,supertabular,titlesec,multicol,multirow}
\geometry{scale=0.9}
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{4pt}{3pt}
\usepackage[unicode,draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\usepackage{fontawesome5}

\newcolumntype{C}{>{\centering\arraybackslash}X}

\newenvironment{joblong}[2]
  {\begin{tabularx}{\linewidth}{@{}l X r@{}}\textbf{#1} & \hfill & #2 \\[-2pt]\end{tabularx}
   \begin{minipage}[t]{\linewidth}\begin{itemize}[nosep,leftmargin=1em,itemsep=1pt,label=--]}
  {\end{itemize}\end{minipage}}

\setlength{\parskip}{2pt}

\begin{document}
\pagestyle{empty}

%----------------------------------------------------------------------------------------
% TITLE
%----------------------------------------------------------------------------------------
\begin{tabularx}{\linewidth}{@{}C@{}}
\Huge{Fahad Ali Khan} \\[4pt]
{\small
\href{https://github.com/Fahad-Ali-Khan-ca}{\raisebox{-0.05\height}\faGithub\ Fahad-Ali-Khan-ca} \;|\;
\href{https://www.linkedin.com/in/fahad-ali-khan-59a182228/}{\raisebox{-0.05\height}\faLinkedin\ Fahad Ali Khan} \;|\;
\href{mailto:Fahad_Ali_Khan.ca@outlook.com}{\raisebox{-0.05\height}\faEnvelope\ \texttt{Fahad\_Ali\_Khan.ca@outlook.com}} \;|\;
\raisebox{-0.05\height}\faMobile\ +1-437-882-8481
}
\end{tabularx}

%----------------------------------------------------------------------------------------
% SUMMARY
%----------------------------------------------------------------------------------------
\section*{Summary}
Software Engineer with experience across \textbf{software development}, \textbf{automation}, and \textbf{testing}. Built API-driven applications and internal tools using \textbf{Python}, \textbf{TypeScript/JavaScript}, \textbf{Node.js}, and \textbf{C\#}, with hands-on experience in CI/CD, debugging, and technical documentation. Strong problem-solver who learns quickly, collaborates well in Agile teams, and is ready to ramp rapidly into client-facing work across software engineering, cloud, or quality engineering tracks.

%----------------------------------------------------------------------------------------
% EDUCATION
%----------------------------------------------------------------------------------------
\section*{Education}
\textbf{Bachelor of Engineering (Software Engineering)} \hfill Aug 2025 \\
Seneca Polytechnic — North York, ON \hfill \textit{President’s Honour List (Fall 2023)}

%----------------------------------------------------------------------------------------
% SKILLS
%----------------------------------------------------------------------------------------
\section*{Technical Skills}
\textbf{Programming:} Python, TypeScript/JavaScript, C\#, C++ (C++20), Java fundamentals, SQL \\
\textbf{Web \& Backend:} React 18, Next.js, Node.js/Express, REST APIs, JSON, authentication \& role-based access \\
\textbf{Testing \& QA:} PyTest, JUnit, manual/regression testing, validation checks, test case design \\
\textbf{Cloud \& DevOps:} AWS (EC2, Lambda, RDS, S3), Git, GitHub Actions CI/CD, Docker, Kubernetes concepts \\
\textbf{Ways of Working:} Agile/Scrum, Jira, Confluence, documentation, cross-functional communication

%----------------------------------------------------------------------------------------
% EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Work Experience}

\begin{joblong}{Software Developer Intern — Project Human City}{Jan 2025 -- Apr 2025}
\item Built and deployed \textbf{REST APIs} using \textbf{Node.js/Express} on \textbf{AWS (EC2, Lambda, RDS)} to support business workflows and internal tools.
\item Automated build, test, and deployment steps through \textbf{GitHub Actions CI/CD}, reducing deployment time by 40\% and improving release consistency.
\item Developed user-facing dashboards and workflow tools with \textbf{React + TypeScript}, improving usability and responsiveness.
\item Collaborated in Agile sprints with cross-functional stakeholders to deliver tested, maintainable changes from requirements through release.
\end{joblong}

\vspace{3pt}

\begin{joblong}{Software Engineer Intern — Digm Labs}{May 2024 -- Aug 2024}
\item Built backend services and integrations in \textbf{Python (Django REST)} and \textbf{Node.js}, supporting reliable API-driven workflows.
\item Improved software quality through automated testing (\textbf{PyTest/JUnit}), achieving 90\% code coverage for critical paths.
\item Supported production debugging using \textbf{CloudWatch + Splunk}, analyzing failures and documenting fixes to reduce repeat incidents.
\item Contributed to clear engineering documentation and repeatable validation steps that improved maintainability and handoffs.
\end{joblong}

\vspace{3pt}

\begin{joblong}{Software Developer Intern — Diginautical}{Sep 2023 -- Dec 2023}
\item Built internal automation and validation tooling in \textbf{C\#} and \textbf{NI TestStand}, reducing manual effort and improving repeatability.
\item Debugged execution issues across tooling workflows, implemented targeted fixes, and improved diagnostics for faster issue resolution.
\item Created and updated technical documentation and work instructions to support consistent execution and smoother onboarding.
\end{joblong}

\vspace{-2pt}

%----------------------------------------------------------------------------------------
% PROJECTS
%----------------------------------------------------------------------------------------
\section*{Projects}

\begin{tabularx}{\linewidth}{@{}l r@{}}
\textbf{AeroGuard Customs — AI CV + LLM Workflow Platform (React/Node)} & \hfill \href{https://github.com/InderParmar/aeroguard-customs}{\faGithub} \\[2pt]
\multicolumn{2}{@{}X@{}}{Built a workflow-focused platform displaying real-time computer vision outputs and LLM-generated summaries. Emphasized reliable API integration, clear user experience, and maintainable frontend/backend collaboration.}\\
\end{tabularx}

\vspace{-2pt}

\begin{tabularx}{\linewidth}{@{}l r@{}}
\textbf{EnglishFormatter — Workflow Automation CLI (C++20)} & \hfill \href{https://github.com/Fahad-Ali-Khan-ca/EnglishFormatter}{\faGithub} \\[2pt]
\multicolumn{2}{@{}X@{}}{Built a structured CLI tool that automates formatting, summarization, and paraphrasing workflows through an external LLM API, with strong validation and reproducible developer workflows.}\\
\end{tabularx}

\end{document}